Storing messages with multipartite neural cliques

### 2014-07-16 Articles/article.tex
...

	Let $\mathcal{M}$ be a set of messages of length $c$ over the alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ and $m = | \mathcal{M} |$. Messages in $\mathcal{M}$ are stored in an undirected unweighted graph, or neural network, of $c \cdot l$ vertices or units. Messages are considered independent and identically distributed.

@@

		Intuitively the choice of $w = a$ is optimal (it it is the most natural with $w = 1$).
		The following is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
		\begin{algorithm}
		\caption{$w$-sum of sum \label{asumsum}}
		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to S}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are identically distributed, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$. Since messages are independent, the density $d$, which is the probability for an edge to be in the network, can be expressed like this :

@@

	We define the efficiency of the network relatively to the hardness of the problem (how much it is efficient compared to a perfect associative memory). A perfect associative memory would use exactly the same number of bits than the original messages and recover messages by maximum likelihood (ambiguities causing errors). Efficiency is the amount of information retrieved divided by the hardness of the problem.

@@

	The maximum information that can be stored in the network is therefore $\eta = \max_x \eta_x $.

@@

	The probability for all good neurons of a correct cluster (resp. of an erroneous cluster) to achieve a score equal or greater than $x$, with at least one having a score of $x$ is $P_{ac} (x) = \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = x)^k P(n_{agc} > x)^{a-k}$ (resp. $P_e(x) = \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k}$)

@@

	\section{Resilience}
	%Spéculations en Français 
	%Peut-être un intérêt pour cluter based associative memories build from unreliable storage : si une arête porte moins d'info, on peut peut-être en supprimer plus (mais rajout ?!)

	As information on a message is shared across connections with multiple activated units per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges. $v_c$ will indicate a correct unit that should be activated, $v$ the other type of units.

@@

	%gamma = infini meilleur sur une itération
	With probability $1 - \psi$, the correct vertex is still connected to a given activated unit in an intact cluster. Thus $P(n_{v_c} = x ) = {a (c_k-1) \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e -1) - x }$

@@

	Sans tenir compte du choix au hasard si plus sont activés. Pour une itération $\gamma = \infty$. Pour plusieurs $\gamma = 1$.

@@

	If $\gamma$ is big enough,
	$P(\mbox{no other vertex activated in this cluster})= \sum_{x = 1}^{a (c - c_e)} P_c(x) P(n_v < x)^{l-a}$%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$

@@

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
		\caption{$\psi = 0.05$, 2 activities per cluster, 8 clusters, 256 units per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{psith}
	\end{figure}

@@

	Figure \ref{comppsi} seems to indicate a linear relationship (after a transition for multiple activities) between $\eta_\psi -\eta_0$ and $\psi$.
	\section{Maximum theoretical efficiency}
		It was shown in \cite{oo} that maximal asymptotic capacity of clique networks is $\log 2$. We generalise this result to multipartite cliques.

>>>>

	Let $\mathcal{M}$ be a set of messages of length $c$ over the alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ (where $a$ is a positive integer) and $m = | \mathcal{M} |$. Messages in $\mathcal{M}$ are stored in an undirected unweighted graph, or neural network, of $c \cdot l$ vertices or units. Messages are considered independent and identically distributed.

@@

		Intuitively the choice of $w = a$ is optimal (it it is the most natural with $w = 1$).
		Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
		\begin{algorithm}[!htb]
		\caption{$w$-sum of sum \label{asumsum}}
		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network, $S$ the number of iterations, $\gamma$ memory effect}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to $S$}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are identically distributed, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$. Since messages are independent, the density $d$, which is the probability for an edge to be in the network, can be expressed as :

@@

	In order to compare different networks using different alphabets, we define the efficiency of the network relatively to the hardness of the problem (how much it is efficient compared to a perfect associative memory). A perfect associative memory would use exactly the same number of bits than the original messages and recover messages by maximum likelihood (ambiguities causing errors). Efficiency is the amount of information retrieved divided by the hardness of the problem.

@@

	The maximum information that can be stored in the network is therefore $\eta = \max_x \eta_x $, which we will define as the efficiency of the network.

@@

	The probability for all good units of a correct cluster (resp. of an erroneous cluster) to achieve a score equal or greater than $x$, with at least one having a score of $x$ is $P_{ac} (x) = \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = x)^k P(n_{agc} > x)^{a-k}$ (resp. $P_e(x) = \sum_{k = 1}^a { a \choose k } P(n_{ge} = x)^k P(n_{ge} > x)^{a-k}$)

@@

	\section{Resilience}
	\subsection{Analytical result}
	%Spéculations en Français 
	%Peut-être un intérêt pour cluter based associative memories build from unreliable storage : si une arête porte moins d'info, on peut peut-être en supprimer plus (mais rajout ?!)

	As information on a message is shared across connections with multiple activated units per cluster, such networks are more resilient to damages (for one message information is carried by $a^2 {c \choose 2}$ edges. $v_c$ will indicate a correct unit that should be activated, $v$ the other type of units.

@@

	%gamma = infini meilleur sur une itération
	We assume $\gamma = \infty$ for one iteration as it prevents activated neurons to be deactivated.
	With probability $1 - \psi$, one correct vertex is still connected to a given activated unit in an intact cluster. Thus $P(n_{v_c} = x ) = {a (c_k-1) \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e -1) - x }$

@@

	%Sans tenir compte du choix au hasard si plus sont activés. Pour une itération $\gamma = \infty$. Pour plusieurs $\gamma = 1$.

@@

	%If $\gamma$ is big enough,
	It follows that $P(\mbox{no other vertex activated in one cluster})= \sum_{x = 1}^{a (c - c_e)} P_c(x) P(n_v < x)^{l-a}$.%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$

@@

	\subsection{Simulations}
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
		\caption{$\psi = 0.05$, 2 activities per cluster, 8 clusters, 256 units per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{psith}
	\end{figure}

@@

	Figure \ref{comppsi} seems to indicate a linear relationship (after a transition for multiple activities) between $\eta_\psi -\eta_0$ and $\psi$.
	\section{Maximum theoretical efficiency}
		It was shown in \cite{Palm1980} that maximal asymptotic capacity of Willshaw networks is $\log 2$. We adapt this result to multipartite clique clustered networks.
